A generalized definition of multidimensional item response theory parameters

### 2023-02-16 output/paper_draft/paper_M2PLM_parameters.Rmd
notacion

Let's consider the standard basis $`r LS_STD_BASIS_EQ`$ in $`r LATENT_SPACE`$.
We can write all $`r TRAIT_VEC_IN_LS`$ as a linear combination of each basis,
$`r LS_BASIS`$ or $`r LS_STD_BASIS`$.
Therefore, we have both representations: $`r TRAIT_VECTOR_DEF_BASIS_EQ`$, and
$`r TRAIT_VECTOR_DEF_STD_BASIS_EQ`$, where $`r TRAIT_COORDS_EQ`$ and
$`r TRAIT_COORDS_STD_EQ`$.

>>>>

Let's consider the standard basis $`r LS_STD_BASIS_EQ`$ in $`r LATENT_SPACE`$.
We can write all $`r TRAIT_VEC_IN_LS`$ as a linear combination of each basis,
$`r LS_BASIS`$ or $`r LS_STD_BASIS`$.
Therefore, we have both representations: $`r TRAIT_VECTOR_DEF_BASIS_EQ`$, and
$`r TRAIT_VECTOR_DEF_STD_BASIS_EQ`$. From now on we  will note  $`r TRAIT_COORDS_EQ`$ and
$`r TRAIT_COORDS_STD_EQ`$.
